Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Ajout explication interet gabriel
Ajout d'une illustration de voronoi

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_graphs/Delaunay_circumcircles_vectorial.svg.png}
    \caption{Example of a Delaunay triangulation}
    \label{del_tri}
\end{figure}

@@

>>>>

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
    \label{del_tri}
\end{figure}

@@

Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration for bad neighbouring connexions.
